Imperfect slope measurements drive overestimation in geometric cone model of lake and reservoir depth

### 2021-12-06 manuscript/manuscript.Rmd
title fix
fight with acknowledgements
typo fix

---
title: Imperfect slope measurements drive overestimation in geometric cone model of waterbody depth

@@

\begin{figure}[H]
  \begin{center}
    \includegraphics[width=0.45\textwidth,keepaspectratio]{../figures/00_map_bathy-1.pdf}
  \end{center}
  \caption{Map of study lakes showing A) lake e maximum depth measurements, B) cross-section shape class, and C) reservoir classification. The distribution of lake depths from panel A is reported in Figure S4.}\label{fig2}
\end{figure}

>>>>

---
title: Imperfect slope measurements drive overestimation in geometric cone model of lake and reservoir depth

@@

\begin{figure}[H]
  \begin{center}
    \includegraphics[width=0.45\textwidth,keepaspectratio]{../figures/00_map_bathy-1.pdf}
  \end{center}
  \caption{Map of study lakes showing A) lake maximum depth measurements, B) cross-section shape class, and C) reservoir classification. The distribution of lake depths from panel A is reported in Figure S4.}\label{fig2}
\end{figure}
